\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
small corrections

In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}. In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem's mathematical formulation and solutions.

@@

\medskip
As can been seen so far there is %from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
%\ref{fig:2c_homoheleshaw_10} there is 
a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements. %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} 
They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}. %\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.  
 Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps. In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation. The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.

>>>>

In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}. In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.

@@

\medskip
As can been seen so far there is %from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
%\ref{fig:2c_homoheleshaw_10} there is 
a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements. %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} 
The third case is of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}. %\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.  
 Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps. In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation. The importance of this set-up is to understand how the simulation works and whether the flow pattern of the fingers follows the experimental results. Also how the fingers will be developed under different permeability schemes as these has already been experimentaly tested.
